Covariate Analysis of ROSMAP Reprocessed counts

### 2020-12-15 code/2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd
recommit

CODE <- syn_temp$store(synapseclient$Folder(name = "ROSMAP", parentId = parentId))

@@

createAndKnitToFolderEntityClient(file = "ROSMAP_Regress_hg38.Rmd",
                                          parentId ="syn21277617",
                                          folderName = 'ROSMAP')

>>>>

CODE <- syn_temp$store(synapseclient$Folder(name = 'Full_RosMap_OldCode', parentId = parentId))

@@

createAndKnitToFolderEntityClient(file = "2020_12_09_ROSMAP_FullCohort_Regress_hg38.Rmd",
                                          parentId ="syn23640229",
                                          folderName = 'ROSMAP')
